---
title: "1. Empirical Motivation"
author: "James Orr, Jeremy Piggott, Andrew Jackson, Michelle Jackson, Jean-Francois Arnoldi"
output:
   html_notebook:
     code_folding: hide
     theme: flatly
     toc: true
     toc_depth: 4
     number_sections: no
---

### Introduction 

This notebook contains the code for the analysis and plotting related to empirical motivation section of our paper: "Variability of functional and biodiversity responses to perturbations is predictable and informative" by James A. Orr, Jeremy J. Piggott, Andrew L. Jackson, Michelle C. Jackson and Jean-François Arnoldi.

Here, we compare the observations of different community metrics (measures of function and of diversity) from a large database of global change experiments in microbial soil systems (Zhou et al 2020, Nature Communications). Each row in the database is the observation of a perturbation (made up of single or multiple global change factors). The columns contain responses of many different community metrics. The data set has 1235 observations and 91 variables. The community metrics that are reported include measures of alpha diversity (e.g., richness, shannon, chao), broad ecosysetem functions (e.g., total biomass, respiration), and narrow ecosystem functions (i.e., specific enzymes). The goal is to create a heatmap showing the proportion of mismatches between different community metrics. We will sort the rows and columns of the heatmap a priori based on a mechanistic understanding of what the community properties are measuring (diversity, broad functions, narrow functions).

### Set up environment and load data

```{r, echo=TRUE, results='hide'}
# Code runs on R version 4.3.1 

#### Clear  environment 
rm(list = ls())         

#### Required packages
library(tidyverse)        # for data organization and manipulation
library(plotrix)          # for gradient.rect function
library(reshape)          # for melt function (to plot heatmap)

zhou_data <- read.csv("Zhou et al 2020 Data.csv", header = T)
```

### Heatmap of mismatches (Figure 1A)

First I'll create a function that takes two community metrics, finds all of the rows in the database where both of these metrics are reported, then reports the proportion of mismatches. If the two variables are the same (diagonals of the heatmap) I return 0 (there are no mismatches). If there are less than 10 rows where the two variables are both reported I return NA as this isn't enough data to give a fair estimate of the proportion of mismatches. 

```{r}

mismatches <- function(data, X, Y, min_obs){
  
  if (X==Y){
    return (0)
  }
  
  else {
  
  temp <- data %>%
    select(X, Y) %>%
    drop_na() %>%
    mutate(mismatch = ifelse(sign(.[,1]) == sign(.[,2]), 0, 1))
  
  if (nrow(temp) < min_obs){
    return (NA)
  }
  
  else {
  
  return (sum(temp$mismatch)/nrow(temp))
}}}

```

Next I run a loop within a loop over the list of variables we want in the heatmap - for all variables I calculate mismatches with all other variables. 

The full list contains all community properties reported in the dataset (n=21) and is ordered by "narrow functions" (and their sub groupings), "broad functions", and "diversity metrics". 

The short list (n=13) was determined by removing variables from the full list that were causing many NAs (i.e. they were rarely reported and/or were rarely reported in combination with other variables) until there were no NA values in the heatmap.


```{r}

# all community metrics sorted a priori 
full_list = c(
              # Narrow Functions
              "PO", "PER", 
              "AG", "BG", "CEL", "XYL", "Invertase",
              "NAG", "LAP", "Urease",
              "AP",
              
              # Broad Functions
              "MicrobialBiomass", "Respiration", "Nmin", 
              "Nitrification", "Denitrification", "Nfixation",
              
              # Diversity Metrics 
              "Chao", "ACE", 
              "Shannon", "OTU")

# community metrics where there are at least 10 comparisons between all pairs
short_list = c( 
         "PO", "PER", 
         "AG", "BG", "CEL", "XYL", #"Invertase",
         "NAG", #"LAP", #"Urease",
         "AP",
         
         "Respiration", "MicrobialBiomass", #"Nmin",
         #"Nitrification", "Denitrification", "Nfixation",

         "Chao", #"ACE", 
         "Shannon", "OTU")

# Names on the axes of the heatmap. 
short_list_names = c("Phenol oxidase", "Peroxidase",
                     "Alpha-glucosidase", "Beta-glucosidase",
                     "Cellobiohydrolase", "Beta-xylosidase",
                     "N-acetyl-beta-glucosaminidase",
                     "Phosphatase",
                     "Respiration", "Biomass", 
                     "Chao index", "Shannon index", "Richness")


########## Full list ###########

my_vec_a = c()

for (j in full_list){
  
  for (i in full_list){
  new_value <- mismatches(zhou_data, j, i, 10)
  my_vec_a <- c(my_vec_a, new_value)
}}

mismatch_matrix_a <- matrix(my_vec_a,nrow=length(full_list))
rownames(mismatch_matrix_a) <- full_list
colnames(mismatch_matrix_a) <- full_list


########## Short list ###########

my_vec_b = c()

for (j in short_list){
  
  for (i in short_list){
  new_value <- mismatches(zhou_data, j, i, 5)
  my_vec_b <- c(my_vec_b, new_value)
}}

mismatch_matrix_b <- matrix(my_vec_b,nrow=length(short_list))
rownames(mismatch_matrix_b) <- short_list_names
colnames(mismatch_matrix_b) <- short_list_names

```

Full list (n = 21) 

```{r, fig.height=6, fig.width=7}

data_melt <- melt(mismatch_matrix_a) 

ggplot(data_melt, aes(X1, X2)) +                           
  geom_tile(aes(fill = value)) +
  scale_x_discrete(guide = guide_axis(angle = 90)) +
  scale_fill_gradient2(low = rgb(0.6, 0.65, 1), high = rgb(1, 0.1, 0.1), mid = "white", 
   midpoint = 0.5, limit = c(0,1), space = "Lab", 
   name="Mismatches")
```
Short list (n = 13) 

```{r, fig.height=6, fig.width=7}
data_melt <- melt(mismatch_matrix_b) 

ggplot(data_melt, aes(X1, X2)) +                           
  geom_tile(aes(fill = value)) +
  scale_x_discrete(guide = guide_axis(angle = 90)) +
  scale_fill_gradient2(low = rgb(0.6, 0.65, 1), 
                       high = rgb(1, 0.1, 0.1), 
                       mid = "white", 
   midpoint = 0.5, limit = c(0,1), space = "Lab", 
   name="Mismatches") +
  theme_minimal()
```

Get number of observations in filtered dataset

```{r}
filtered <- zhou_data %>%
  # select the 13 community properties
  select(short_list) %>%
  # remove rows that have only one or no observations (i.e., not in heatmap)
  filter(rowSums(is.na(.)) < 12)
```

Get the number of experiments where OTU was the only measure of diversity 

```{r}
OTU_only <- zhou_data %>%
  select(OTU, Chao, ACE, Shannon) %>%
  filter(!is.na(OTU) & is.na(Chao) & is.na(ACE) & is.na(Shannon))
```


### Specific examples (Figure 1B)

Here we pick out specific examples to plot the raw data for (code to create the exact plots found in the paper is in 2. Simulations). 

```{r, fig.height=3, fig.width=9}
par(mfrow = c(1, 3))
######### Biomass - Respiration ########

sub <- zhou_data %>%
  select(MicrobialBiomass, Respiration) %>%
  drop_na() %>%
  mutate(mismatch = ifelse(sign(MicrobialBiomass) == sign(Respiration), 0, 1)) 

prop_mismatch <- sum(sub$mismatch)/nrow(sub)
maxX = max(abs(sub$MicrobialBiomass))
maxY = max(abs(sub$Respiration))
sub$mismatch <- as.factor(sub$mismatch)

write_csv(sub, "output/biomass_respiration.csv")


plot(sub$MicrobialBiomass, sub$Respiration, 
     xlab = "Response of Biomass", ylab = "Response of Respiration",
     xlim = c(-maxX, maxX), ylim = c(-maxY, maxY), pch = 20, 
     col = c(rgb(0.4,0.5,1), rgb(1, 0.3, 0.3))[sub$mismatch],
     cex.lab = 1.5)
abline(h = 0, lty = 2)
abline(v = 0, lty = 2)
mtext(paste("Mismatch = ",round(prop_mismatch, 2)," \nn = ",nrow(sub)," ", sep = ""),
      side = 3, line = -2.4, adj = 1, cex = 0.8)

######### Biomass - Richness ########

sub <- zhou_data %>%
  select(MicrobialBiomass, OTU) %>%
  drop_na() %>%
  mutate(mismatch = ifelse(sign(MicrobialBiomass) == sign(OTU), 0, 1)) 

prop_mismatch <- sum(sub$mismatch)/nrow(sub)
maxX = max(abs(sub$MicrobialBiomass))
maxY = max(abs(sub$OTU))
sub$mismatch <- as.factor(sub$mismatch)

write_csv(sub, "output/biomass_richness.csv")

plot(sub$MicrobialBiomass, sub$OTU, 
     xlab = "Response of Biomass", ylab = "Response of Richness",
     xlim = c(-maxX, maxX), ylim = c(-maxY, maxY), pch = 20, 
     col = c(rgb(0.4,0.5,1), rgb(1, 0.3, 0.3))[sub$mismatch],
     cex.lab = 1.5)
abline(h = 0, lty = 2)
abline(v = 0, lty = 2)
mtext(paste("Mismatch = ",round(prop_mismatch, 2)," \nn = ",nrow(sub)," ", sep = ""),
      side = 3, line = -2.4, adj = 1, cex = 0.8)

######### CHAO - XYL ########

sub <- zhou_data %>%
  select(Chao, AP) %>%
  drop_na() %>%
  mutate(mismatch = ifelse(sign(Chao) == sign(AP), 0, 1)) 

prop_mismatch <- sum(sub$mismatch)/nrow(sub)
maxX = max(abs(sub$Chao))
maxY = max(abs(sub$AP))
sub$mismatch <- as.factor(sub$mismatch)

write_csv(sub, "output/chao_AP.csv")

plot(sub$Chao, sub$AP, 
     xlab = "Response of Chao index", ylab = "Response of Phosphatase",
     xlim = c(-maxX, maxX), ylim = c(-maxY, maxY), pch = 20, 
     col = c(rgb(0.4,0.5,1), rgb(1, 0.3, 0.3))[sub$mismatch],
     cex.lab = 1.5)
abline(h = 0, lty = 2)
abline(v = 0, lty = 2)
mtext(paste("Mismatch = ",round(prop_mismatch, 2)," \nn = ",nrow(sub)," ", sep = ""),
      side = 3, line = -2.4, adj = 1, cex = 0.8)


```

